Topic Modeling of News

### 2017-10-24 paper/R/webhoseio_prepare.Rmd
new
add more cleaning

@@

>>>>

## Count number of terms in a string
```{r}
df %>% filter(site != "zdf.de") -> df

df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
```

@@

## Save by Site
```{r}
df %>% filter(site=="stern.de") %>% write.csv(.,file = "../output/stern.csv")
df %>% filter(site=="focus.de") %>% write.csv(.,file = "../output/focus.csv")
df %>% filter(site=="zeit.de") %>% write.csv(.,file = "../output/zeit.csv")
df %>% filter(site=="wdr.de") %>% write.csv(.,file = "../output/wdr.csv")
df %>% filter(site=="spiegel.de") %>% write.csv(.,file = "../output/spiegel.csv")
df %>% filter(site=="welt.de") %>% write.csv(.,file = "../output/welt.csv")
df %>% filter(site=="handelsblatt.com") %>% write.csv(.,file = "../output/handelsblatt.csv")
df %>% filter(site=="tagesschau.de") %>% write.csv(.,file = "../output/tagesschau.csv")
df %>% filter(site=="swr.de") %>% write.csv(.,file = "../output/swr.csv")
df %>% filter(site=="bild.de") %>% write.csv(.,file = "../output/bild.csv")
df %>% filter(site=="ndr.de") %>% write.csv(.,file = "../output/ndr.csv")
```

## Load by site
```{r}
focus <- read.csv("../output/focus.csv")
#spiegel <- read.csv("../output/spiegel.csv")
#bild <- read.csv("../output/bild.csv")

df_reduced <- rbind(focus, spiegel, bild)
```

```{r}
save(df_reduced, file="../output/df_reduced")
```
